%!TEX root = ../template.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% chapter4_PrototypingPerf.tex
%% NOVA thesis document file
%%
%% Chapter with the Prototyping and Performance Evaluation Results part
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\typeout{NT FILE chapter4_PrototypingPerf.tex}

\chapter{Prototyping and Performance Evaluation Results}\label{cha:chapter4_PrototypingPerf}

So neste capitulo e que se deve descrever a operacao do circuito.

It should be noted that, for the top and bottom FET selection stage, the Si7212DN model suggested is a double FET in one package. The CSD17308Q3 substituting model is a single-channel FET (only one per package), and therefore two units had to be acquired -- Section~\ref{sec:3211_LTC4012}.

\section{PCB Manufacture}\label{sec:41_PCBmanufacture}

\section{Component Acquisition}\label{sec:42_ComponentAcquisition}

%ate agora foram os unicos MOSFETs que nao disse o nome:

%como nao foi relevante, ate agora ainda nao disse que MOSFETs selecionei para o power switch: Q4 e Q5.
%Q3, Q10, Q6, Q8 -- BQ29209

% AP64501:
Recalling Section~\ref{sec:3214_AP64501}, it is stated that the closest commercially available values of 11k$\Omega$ and 2.7k$\Omega$ were selected for R10 and R13, respectively, at the prototyping phase. Following expressions (\ref{eq:R10}) and (\ref{eq:R13}), these values allow the expected $V_{ON}$ and $V_{OFF}$ values.
    % inductor L2:
    Meter Eq. 9 do datasheet do AP64501;
    
    Peak current determines the required saturation current rating, which influences the size of the inductor. Saturating the inductor decreases the converter efficiency while increasing the temperatures of the inductor and the internal power MOSFETs. Therefore, choosing an inductor with the appropriate saturation current rating is important. 
    It is recommended by \cite{AP64501} the selection of an inductor value between $1 \mu$H to $10 \mu$H, and therefore, taking into account the values presented in Table~\ref{tab:AP64501_recommended_values}, an inductor of $3.6 \mu$H was selected. It is also advised to select an indcutor with a DC current rating of at least 35\% higher than the maximum 5A load current of the AP64501, which corresponds to 6.75A.
    For highest efficiency, the inductor's DC resistance should be less than 10mOhm. Use a larger inductance for improved efficiency under light load conditions.


% CM4:
    At just 40mm $\times$ 55mm and 4.7mm deep, the form factor of the CM4 is one of its biggest advantages, since it allows designers to fit it in almost all designs.

    %HDMI routing:
    HDMI signals should be routed as 100Ohm differential pairs. Each signal within a pair should ideally be matched to better than 0.15mm. Pairs don't typically need any extra matching, as they only have to be matched to 25mm.

    %USB routing:
    The differential pair should be routed as a 90Ohm differential pair. The length of the P/N signals should ideally be matched to better than 0.15mm.

    6. The port is capable of being used as a true USB On-The-Go (OTG) port. While there is no official documentation, some users have had success making this work. The USB\_OTG\_ID pin is used to select between USB host and device that is typically wired to the ID pin of a Micro USB connector. To use this functionality it must be enabled in the OS. If using either as a fixed slave or fixed master, please tie the USB\_OTG\_ID pin to ground. tentei isto e nao deu.


% LAN9514:
    However, USB has the advantage of allowing hot-swapping, making it useful for mobile peripherals, including drives of various kinds. -- mesmo que digam isto ja é possivel por natureza do USB, eu ainda tentei fazer o que dizia no datahseet do LAN9514 para dar enable ao hot-swapping, mas continuou sem funcionar.

\section{Prototype Assembly}\label{sec:43_PrototypeAssembly}

\section{Functional Testing and Results}\label{sec:44_FunctionalTesting}